Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-11 manuscript.tex
Rewording the introduction

% utilizing the combo of small satellite and low thrust propulsion offers new mission scenarios 
With reduced development intervals and decreased launch costs, small satellites have gained increased attention as a cost effective means of scientific and technologic development. 
Furthermore, these cubesats are easily launched as secondary payloads rather than requiring a dedicated launch.
The merger of small satellites with miniature electric propulsion enables inexpensive and responsive missions requiring large changes in orbital energy or extended mission lifespan.
Recent developments in miniature electric propulsion offer the potential for new research opportunities for small spacecraft~\cite{haque2013}.
The advancements in miniature electric propulsion allows for greater flexibility in the deployment of cubesats as secondary payloads.
Without the explicit requirement of a dedicated launch trajectory, cubesats are able to exploit a much wider range of possible mission designs~\cite{folta2015}.
With the potential for more demanding missions, even greater importance is placed on the mission design to ensure that optimal trajectories satisfy mission requirements. 
In addition, non-Keplerian orbits and multi-body dynamics have been shown to allow for a much greater range of potential missions at a reduced energy cost~\cite{folta2015,koon2011}.
Future space missions are increasing in complexity and will require new classes of orbits that are not possible via the traditional patched-conic approach~\cite{ross2006,gomez2001}.
Optimally combining the structure of the dynamic environment with low-thrust propulsion systems is vital for future mission success.

>>>>

% utilizing the combo of small satellite and low thrust propulsion offers new mission scenarios 
Recent developments in miniature electric propulsion and small satellites now offer the potential for new research oppportunities~\cite{folta2015,haque2013}.
The potential for more demanding missions places an even greater importance on the mission design to ensure that optimal trajectories satisfy mission requirements~\cite{folta2015,koon2011,ross2006,gomez2001}. 
Optimally combining the structure of the dynamic environment with low-thrust propulsion systems is vital for future mission success.
